Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex
CERTAIN THAT.
THAT.

THAAAAAAAAAAAAAAAAAAAAAAAAT.

Once a full Coq proof of noninterference exists, a next step would be to
integrate this proof and all of the related definitions into a verified type
checking program, which could be integrated into a verified compiler.  We
already know that a full verified compiler has been done for C, and this gives
us hope that it would be possible to implement something similar for a language
like Jif.

With a verified compiler for such a language, it would be possible to implement
a compiler that produced proofs of noninterference to be carried around with the
compiled program.  This would be interesting in distributed settings where we
would like to ship code around to others to run on their own machines.  There is
already a paper on the subject of mobile code for the Fabric
language~\cite{liu2009fabric}, a distributed computing variant of Jif,
discussing the problem of ``mobile code'', which operates by having the client
compile the code themselves~\cite{arden2012sharing}.  A proof-carrying code
system could possibly remove the need for the target machine to compile the code
themselves in order to ensure trust requirements are met.

Another use of a verified compiler would be the ability to verify extensions to
the language.  For example, the Jif and Fabric programming languages are
actively worked on and has seen multiple extensions over the years.  Although
it's pretty certain extensions to these languages that are published are
correct, requiring these extensions to be added to a verified compiler would
help ensure that the language updates will not invalidate pre-existing security
properties of the language, because adding the extension would require adding
code to cover the additional cases in the proofs.

\todo{more.}

>>>>

Once our noninterference proof has been sucessfully mechanized for \langName, we will incrementally enhance the features of \langName, adding in absent constructs such as bind, references, and exceptions.  We will then re-state and re-prove the noninterference result in a language very much like \origLang.

Once a full Coq proof of noninterference exists, a next step would be to
integrate this proof and all of the related definitions into a verified type
checking program, which could be integrated into a verified compiler.  We
already know that a full verified compiler has been done for C, and this gives
us hope that it would be possible to implement something similar for a language
like Jif.  We are aware that any such effort would require many person-years of effort to complete, but we remain convinced that such an effort would be a worthwhile initiative.

With our verification effort complete, it would be possible to implement
a compiler that produced proofs of noninterference to be carried around with the
compiled program.  This would be interesting in distributed settings where we
would like to ship code around to others to run on their own machines.  There is
already a paper on the subject of mobile code for the Fabric
language~\cite{liu2009fabric}, a distributed computing variant of Jif,
discussing the problem of ``mobile code'', which operates by having the client
compile the code themselves~\cite{arden2012sharing}.  A proof-carrying code
system could possibly remove the need for the target machine to compile the code
themselves in order to ensure trust requirements are met.

Another use of a verified compiler would be the ability to verify extensions to
the language.  For example, the Jif and Fabric programming languages are
actively worked on and have seen multiple extensions over the years.  Although
it's pretty certain that extensions to these languages that are published are
correct, errors to creep into even the most scrutinized of paper results (as we
have observed in this project), and so requiring these extensions to come with
mechanized proofs of correctness before incorporation into a verified compiler
would help ensure that the language updates will not invalidate pre-existing
security properties of the language.
